---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  root.dir = "data"
)
```

# Lab.Data.Prep

<!-- badges: start -->
[![R-CMD-check](https://github.com/jessjorge/Lab.Data.Prep/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jessjorge/Lab.Data.Prep/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The Lab Data Prep package is designed to streamline some common laboratory data prep tasks. Rat study data is often delivered in a format that is difficult to understand and work with; however, many of the data cleaning tasks are routine. This package consolidates these routine tasks into a few simple functions that can be called with ease, and provides a plotting utility function to use after data conversion. What formerly took a few hundred lines of code is now just a few function calls away. 

## Installation

You can install the development version of Lab.Data.Prep from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jessjorge/Lab.Data.Prep")
```

## Example

Med PC is the program used for data collection in this laboratory setting. The **mpc** function produces an mpc dataframe.

```{r example}
library(Lab.Data.Prep)

# Extract files with a given subject number
subs<-extract("EB",c(11))
```

```{r}
# Call mpc to create a med pc 
df<-mpc(subs[[1]],"d")
```

To make a dataframe, we require a dictionary of event-type/event-name pairs. It is reccomended to first define the dictionary, then pass it into the function.

```{r}
# Event type = Event Name
vars <- c(
  "0.2" = "target",
  "0.51" = "alternative"
)

new_df<-var_def(df, vars, cumulative = TRUE)
```

All that's left is to call a constructor function, **select**, then pass it into the plotting function for an easy step function experience!

```{r}
isolate<-select(new_df, "target  (cumulative)")
plot(isolate)
```
