---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  root.dir = "inst/extdata"
)
```

# Lab.Data.Prep

<!-- badges: start -->
[![R-CMD-check](https://github.com/jessjorge/Lab.Data.Prep/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jessjorge/Lab.Data.Prep/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The Lab Data Prep package is designed to streamline some common laboratory data prep tasks for researchers utilizing Med-PC software. Med-PC data is delivered in a format that is difficult to understand and work with; however, many of the data cleaning tasks are routine. This package consolidates these routine tasks into a few simple functions that can be called with ease, and provides a plotting utility function to use after data cleanup. What formerly took a few hundred lines of code is now just a few function calls away. 

## Installation

You can install the development version of Lab.Data.Prep from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jessjorge/Lab.Data.Prep")
```

## Example

To import Med-PC data files, the **extract()** function can be called. This function is designed to extract files for a single experiment where all subjects have a common prefix. If subjects do not share a common prefix, the function can be called for individual subjects. The subject number prefix is supplied as the first argument, in this case "EB". The subject id numbers can be supplied as either a single numeric, or a vector of numeric to extract multiple subjects. Lastly, the location of the data files are supplied in a filepath argument. **extract()** returns an r data frame for each mpc file with no change to the original formatting.

```{r example}
library(Lab.Data.Prep)

# Extract files with a given subject number
subs <- extract("EB",11,paste(system.file("extdata", package = "Lab.Data.Prep"),"/", sep = ""))
```

In the current example, we call the **mpc()** function on the **subs** list generated from the **extract()** function. The **mpc()** function takes as arguments a list of data files for a single subject and an array of interest from the original data file. In this case, the **"d"** array has been selected. Below is a snippet of the **"d"** array. The number before the decimal place is a timestamp in centiseconds, and the second number is a unique event identifier.

```{r}
subs[[1]][1]
```

This package is designed to handle arrays that store timestamps with associated event tags as shown above. 

```{r}
# Call mpc to create a med pc
df <- mpc(subs[[1]], "d")
```

The new dataframe has 9 unique, undefined event tags. Each of these numbers corresponds to a unique event type, which will be defined by a practitioner in the form of an R dictionary.

```{r}
unique(df$event_tags)
```

A dictionary in R looks a lot like a vector, but each element consists of a key and a value, separated by an equals sign. The user should define this dictionary as follows and pass it into the var_def function. var_def will take the dictionary and create a new dummy variable (1's \& 0's) column named after each value.

```{r}
# Event type = Event Name
vars <- c(
  "0.111" = "Rat Turned Into a Butterfly",
  "0.2" = "Rat Earns LSD",
  "0.5" = "Rat Fights Snake, Loses",
  "0.51" = "Rat Fights Snake, Wins",
  "0.71" = "Rat Literacy Tests",
  "0.52" = "Water Spiked with Strawberry Wine"
)

new_df <- var_def(df, vars, cumulative = TRUE)
```

Now we take a look at the new dataframe. var_def has created binary variables for each element of the vars dictionary. At each time_stamp, if the event of interest occurred there is a 1 in the corresponding column. If cumulative = TRUE, an additional column for each variable will be created to track running totals of events at each time point.  

```{r}
head(new_df)
```

Now we run **select()** to grab the columns that we want for plotting. Because rats earned a lot of LSD, we are grabbing the "Rat Earned Some LSD  (cumulative)" variable. Note that the variable name must be typed exactly, and there are **two spaces** between the *variable name* and the *(cumulative)* component. 

```{r}
isolate <- select(new_df, "Rat Earns LSD  (cumulative)")
```

Now the data has been transformed and is suitable for cummulative record generation.

```{r}
head(isolate)
```

All that's left is to plot!


```{r}
plot(isolate)
```
